%-------------------------
% Tailored ATS-Optimized LaTeX CV
% Target Role: AI Intern @ Kologic.AI (Hyderabad, India)
% Alignment Focus: Conversational AI, Workflow Automation, Data Intelligence
% Frameworks: STAR & PAR outcome structures
% Fits exactly 1-page full
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{multicol}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins to ensure 1-page compact layout
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{0pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Commands  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{0pt}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Document Header  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
    \begin{center}
        {\Huge\scshape Gopu Abhinav Vamsi} \\ \vspace{2pt}
        Hyderabad, Telangana ~|~ Phone: 8977243888 ~|~ \href{mailto:abhinavvamsi2004@gmail.com}{\underline{abhinavvamsi2004@gmail.com}} \\ \vspace{2pt}
        \small
        \href{https://www.linkedin.com/in/gopu-abhinav-vamsi-0211ab294/}{\faLinkedin\ \underline{LinkedIn}} ~|~
        \href{https://github.com/Abhinavvamsi}{\faGithub\ \underline{GitHub}} ~|~
        \href{https://abhinavvamsi.github.io/abhinav-portfolio/}{\faGlobe\ \underline{Portfolio}}
    \end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Education  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Gokaraju Rangaraju Institute of Engineering and Technology}{Hyderabad}
      {B.Tech in Computer Science and Engineering (8.2 CGPA)}{Expected Jul 2026}
  \resumeSubHeadingListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Experience  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Credit Saison India}{Bangalore}
      {Machine Learning Intern}{Dec 2024 -- Apr 2025}
      \resumeItemListStart
        \resumeItem{Engineered production-grade predictive machine learning models to simplify and optimize core risk underwriting operations, closely supporting enterprise data intelligence workflows.}
        \resumeItem{Developed scalable automated client application evaluation pipelines for major corporate accounts (\textbf{Airtel, CRED, PhonePe}), ensuring rapid decision delivery and robust compliance tracing.}
        \resumeItem{Performed rigorous feature engineering, target class balancing, and model debugging to guarantee highly reliable operational outcomes across dense transactional datasets.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  PROJECTS  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Personal Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{End-to-End MLOps Pipeline Deployment} ~|~ \textit{Python, Flask, AWS EC2, SQL}}{}
      \resumeItemListStart
        \resumeItem{Built and deployed a secure REST API serving architecture utilizing \textbf{Flask} on \textbf{AWS EC2} to integrate model inference logic with real-time enterprise process automation workflows.}
        \resumeItem{Designed an active logging back-end using \textbf{SQL} to track payload inputs and capture evaluation metrics, ensuring systemic reliability and transparent monitoring for drift analysis.}
        \resumeItem{Successfully delivered scalable hosting configurations capable of concurrent multi-threaded execution while eliminating request dropped-packet artifacts.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{COVID-19 Detection Using CNN} ~|~ \textit{Python, TensorFlow, Keras, OpenCV}}{}
      \resumeItemListStart
        \resumeItem{Developed a deep learning Computer Vision model utilizing \textbf{TensorFlow} to classify automated diagnostic markers, assisting clinical throughput efficiency.}
        \resumeItem{Applied precise image processing and matrix transformations via \textbf{OpenCV} to optimize feature convergence and standardize generalizable loss validations.}
        \resumeItem{Lifted out-of-sample diagnostic validation accuracy substantially from \textbf{74.89\% to 89.34\%}, demonstrating robust analytical problem-solving skills.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Deepfake Visual Media Detector} ~|~ \textit{Python, VGG-19 Deep Networks}}{}
      \resumeItemListStart
        \resumeItem{Fine-tuned a transfer learning neural network architecture to evaluate unverified spatial artifacts, delivering reliable classification on unseen test streams.}
        \resumeItem{Achieved a definitive precision lift across rigorous visual arrays from \textbf{56.43\% to 82.99\%}, demonstrating proactive engineering design execution.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Zomato Customer Segmentation} ~|~ \textit{Python, Pandas, Scikit-Learn, Clustering}}{}
      \resumeItemListStart
        \resumeItem{Executed deep data analysis, missing-value imputation, and statistical modeling on unstructured customer dining records to extract actionable enterprise intelligence.}
        \resumeItem{Deployed \textbf{K-Means clustering} algorithms to map highly localized operational client groupings, enabling dynamic target recommendation logic.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Technical Skills  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Technical Skills}
  \vspace{-7pt}
  \begin{itemize}[leftmargin=0.15in, label={}]\small{\item{
    \textbf{Core Programming}{: Python, C, SQL (Proficient in foundational algorithms and CS optimization)} \\
    \textbf{AI \& Data Intelligence}{: TensorFlow, Keras, Scikit-Learn, Pandas, NumPy, Feature Engineering, Workflow Automation} \\
    \textbf{Systems \& Methodologies}{: AWS, REST APIs, MLOps, System Testing, Debugging, Operational Compliance} \\
    \textbf{Certifications}{: Machine Learning (Udemy), Data Analyst (Udemy), MLOps Architecture (Udemy)} \\
    \textbf{Local Availability}{: Immediately available for full-time on-site engagement in Hyderabad}
  }}
  \end{itemize}

\end{document}
